### 2020-02-23 doc/icfp20/music.tex
better text for music

\paragraph{Pitches}
A \emph{pitch} is a value denoting how high or low a sound is.
In our implementation, pitches have type \texttt{Pitch} and take the
form \texttt{name octave}, where \texttt{name} is a name ranging
over \texttt{c}, \texttt{d}, \texttt{e}, etc. and \texttt{octave} is a
natural number denoting which octave the pitch belongs to.
For instance, the middle C is represented as \texttt{c 5}.

@@

\paragraph{Duration}
\emph{Duration} denotes an unspecified unit of time during which a
sound or silence lasts.
In our implementation, duration (of type \texttt{Duration} is simply
a natural number, denoting the relative length within a bar (such as
whole and half).
When the music is played at a specific tempo, the number is 
multiplied by a velocity and turned into an absolute length.

@@

\paragraph{Notes}
Combining pitches and duration gives us \emph{notes}.
In our implementation, we represent notes as a datatype \texttt{Note}
with two constructors: \texttt{tone} for notes with sound and
\texttt{rest} for those without.

@@

\emph{Intervals} are a concept denoting the difference in pitch
between two notes.
There are 13 kinds of interval within an octave, and these intervals
can be classified from several different perspectives: (i) major or
minor; (ii) consonant or dissonant; and (iii) perfect or imperfect.
We define intervals as a datatype \texttt{Interval}, where each
constructor represents one of the 13 intervals.

>>>>

\paragraph{Pitches}
A \emph{pitch} tells us how high or low a sound is.
This notion is represented as natural numbers (of type
\texttt{Pitch}) in our implementation, with zero representing the
lowest possible sound.
Throughout the paper, we use the notation \texttt{name octave}
for pitches, where \texttt{name} ranges over \texttt{c}, \texttt{d},
\texttt{e}, etc., and \texttt{octave} denotes which octave the pitch
belongs to.
For instance, the middle C is represented as \texttt{c 5}.

@@

\paragraph{Duration}
\emph{Duration} denotes an unspecified unit of time during which
a sound or silence lasts.
In our implementation, duration is again a natural number (of type
\texttt{Duration}), with names such as \texttt{whole}, \texttt{half},
and \texttt{quarter}.
These values are turned into an absolute length when the music is
played at a specific tempo.
As an example, \texttt{whole} has value \texttt{16} and corresponds
to 4 seconds if the tempo is 60 beats per minute.

@@

\paragraph{Notes}
Combining pitches and duration gives us \emph{notes}.
We construct notes (of type \texttt{Note}) with the \texttt{tone}
and \texttt{rest} constructors.
For example, \texttt{tone whole (c 5)} is a whole note whose
sound is the middle C, and \texttt{rest half} is a half rest.

@@

An \emph{interval} represents the difference in pitch between
two notes.
There are 13 kinds of interval within an octave, and these
intervals can be classified from several different perspectives:
(i) major or minor; (ii) consonant or dissonant; and (iii) perfect
or imperfect.
We define intervals as a datatype \texttt{Interval}, where each
constructor represents one of the 13 intervals.
